---
title: "OliviaMP4"
output: github_document
---
```{r}
library(devtools)
library(foofactors)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is a toy package created for expository purposes, for the second edition of [R Packages](https://r-pkgs.org). It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://forcats.tidyverse.org).**

# foofactors    

<!-- badges: start -->
<!-- badges: end -->

Factors are a very useful type of variable in R, but they can also be very aggravating. This package provides some helper functions for the care and feeding of factors.

## Installation

You can install foofactors like so:

``` r
devtools::install_github("390-2020-09-Fall/foofactors")
```
Given two random integers
```{r}
x <- sample(1:10, 1)
y <- sample(1:10,1)
c(x,y)
```

Using fmultiply() to get the product of those two random integers 
```{r}
fmultiply(x,y)
```







